\titleName{}

### 2015-12-07 FinalProject/Tex/paper/paper.tex
added title, fake abstract, keywords, bulleted ideas

% Page heads
\markboth{C. Smith}{TODO A Survey Paper}

% Title portion
\title{TODO A Survey Paper}
\author{Connor Smith
\affil{Brigham Young University}}

\begin{abstract}
This is my abstract.
\end{abstract}

\keywords{TODO, General purpose graphics processing unit, heterogeneous systems,
warp size}

\acmformat{Connor Smith, 2015. TODO A Survey Paper.}

@@

Author's addresses: C. Smith, Electrical and Computer Engineering Department,
Brigham Young University.
\end{bottomstuff}

@@

\section{New Designs}
Warp compression stuff
  Assist warps (CABA)
  Warped Compression
Dynamic tuning
  Coordinated warp scheduling (CAWA)
  Dynamic Thread Block Launch (DTBL)
  Equalizer
  Fine-grain Hardware Worklists (HWWL)
  Variable Warp Size (VWS)
CPU/GPU contention, NoC
  Managing Concurrency in Heterogeneous
Compiler/SW-only design
  Divergence Management
  Locality Aware Mapping
  (x) WeakBehaviorProgrammingAssumptions

>>>>

\newcommand{\titleName}{General-Purpose GPUs and the Challenges of Efficient
Parallel Processing of Heterogeneous Applications}

% Page heads
\markboth{C. Smith}{\titleName{}}

% Title portion
\title{\titleName{}}
\author{Connor Smith
\affil{Brigham Young University}}

\begin{abstract}
TODO This is my abstract. It has many pretty lorem ipsum words. Lorem ipsum
dolor sit amet, consectetur adipiscing elit. Aliquam nec est at nibh tempus
malesuada. Proin eget risus ut arcu imperdiet porttitor nec maximus est. Ut
vulputate gravida arcu vitae molestie. Vivamus tempor semper erat in
condimentum. Vestibulum tincidunt pulvinar dolor, sit amet tincidunt sem
sollicitudin et. Donec ut ultricies nulla, fringilla gravida neque. Sed feugiat
mauris eu enim ultricies, id tincidunt velit semper. Curabitur blandit diam
odio, in mollis risus porttitor eget. Vivamus rutrum enim turpis, eu posuere
nibh mattis porttitor. Aenean mollis augue nec semper porta. Nulla semper vitae
sapien quis commodo. Mauris tempor libero sollicitudin cursus lacinia.
\end{abstract}

\keywords{General purpose graphics processing unit, heterogeneous systems, warp
size, dynamic warp, GPU compression, hardware worklists, locality aware mapping}

\acmformat{\titleName{}.}

@@

Author's address: C. Smith, Electrical and Computer Engineering Department,
Brigham Young University.
\end{bottomstuff}

@@

\section{New Designs}
\begin{itemize}
\item Warp compression stuff
  \begin{itemize}
  \item Assist warps (CABA)
  \item Warped Compression
  \end{itemize}
\item Dynamic tuning
  \begin{itemize}
  \item Coordinated warp scheduling (CAWA)
  \item Dynamic Thread Block Launch (DTBL)
  \item Equalizer
  \item Fine-grain Hardware Worklists (HWWL)
  \item Variable Warp Size (VWS)
  \end{itemize}
\item CPU/GPU contention, NoC
  \begin{itemize}
  \item Managing Concurrency in Heterogeneous
  \end{itemize}
\item Compiler/SW-only design
  \begin{itemize}
  \item Divergence Management
  \item Locality Aware Mapping
  \item (x) WeakBehaviorProgrammingAssumptions
  \end{itemize}
\end{itemize}
